%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com), 2020-2024 moderncv maintainers (github.com/moderncv).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\input{common.tex}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Skills}
\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
\cvtripleitem{category 4}{XYZ}{category 5}{XYZ}{category 6}{XYZ}

\section{Education}  % for 'contemporary' style use optional argument for displaying an icon, e.g. \section[\faGraduationCap]{Education}
\cventry{Apr. 2019 -- Mar. 2022}{Informatics: Games Engineering -- M.Sc.}{TUM School of Computation, Information and Technology}{TU Munich}{Final grade: 1.6}{
  My specialization is in computer vision, machine learning, deep learning, and robotics. I conducted practicals and research projects on autonomous driving and robotic applications, applying my knowledge and skills.
}  % arguments 3 to 6 can be left empty
\cventry{Oct. 2015 -- Mar. 2019}{Informatics: Games Engineering -- B.Sc.}{TUM School of Computation, Information and Technology}{TU Munich}{Final grade: 2.1}{
  I gained a comprehensive understanding of computer science fundamentals, including software engineering, algorithms, mathematics, databases, and distributed systems.
  I specialized in computer graphics, physics simulations, augmented/virtual reality, AI, and autonomous driving.
}  % arguments 3 to 6 can be left empty

\section{Master thesis}
\cventry{Oct. 2021 -- Mar. 2022}{TUM: Chair of Robotics, Artificial Intelligence, and Real-time Systems}{\href{https://github.com/MarcelBruckner/CDN/blob/main/master-thesis.pdf}{Vision-Based Continual Reinforcement Learning for Robotic Manipulation Tasks} \cite{master-thesis}}{TU Munich}{Final grade: 1.0}{I merged techniques from continual learning and reinforcement learning on a single arm robot in a monocular camera setting and developed a hypernetwork-based approach to train the robot using only observations from a single camera. }

\section{Experience}
% \subsection{Vocational}
\cventry{Mar. 2022 -- Today}{\href{https://teamscale.com/publication-author/marcel-bruckner}{Software Consultant}}{CQSE GmbH}{Munich}{}{I advise our customers in establishing effective software quality assurance processes by analyzing their software systems, architecture, used technologies, and their development process, all with a focus on future-proofness and maintainability.}
\cventry{Apr. 2021 -- Sep. 2021}{Student Assistant with a Degree}{TUM: Chair of Robotics, Artificial Intelligence and Real-time Systems}{Munich}{}{I implemented the Online Self-Correcting Calibration Architecture for Multi-Camera Traffic Localization Infrastructure for the  Providentia++ project on the A9 highway. We documented our work in the following publication \cite{paper}.}

\section{Publications}
\cventry{2024}{IEEE Symposium on Intelligent Vehicle}{\href{https://ieeexplore.ieee.org/document/10588435}{An Online Self-Correcting Calibration Architecture for Multi-Camera Traffic Localization Infra.} \cite{paper}}{IEEE}{}{Most vision-based sensing and localization infrastructure today employ conventional area scanning cameras due to the high information density and cost efficiency offered by them. While the information-rich two-dimensional images provided by such sensors make it easier to detect and classify traffic objects with the help of deep neural networks, their accurate localization in the three-dimensional real world also calls for a reliable calibration methodology, that maintains accuracy not just during installation, but also under continuous operation over time. In this paper, we propose a camera calibration architecture that extracts and uses corresponding targets from high definition maps, augment it with an efficient stabilization mechanism in order to compensate for the errors arising out of fast transient vibrations and slow orientational drifts. Finally, we evaluate its performance on a real-world test site and showed to improve the localization accuracy by $50\%$.}

\section{Interests}
\cvitem{Selfhosting}{Homelab for personal services, smart home and home surveillance system}
\cvitem{Sports}{Gym, Disc Golf, Downhill--Biking}
\cvitem{Volunteering}{Passionate Blood--Donor, Foster home for saved stray dogs coming from greece}

\section{Languages}
\cvdoubleitem{German}{Native}{English}{Fluent}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file
% if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.